Multi-level modeling with Openflexo/\FML

### 2022-03-17 4-technology.tex
parallel in naming convention between text and fig.2 => explicit mention of FlexoThings

{\color{red} This paragraph needs a parallel in naming convention between Figure 2 and the text.  FlexoConcept, FlexoBehavior, etc.} A \UML like representation of a simplified metamodel of \FML is provided in Fig.~\ref{fig:mm}. \FML is a language designed to define virtual models. A \emph{virtual model} is composed of a set of \emph{concepts}, while itself being a \emph{concept}. Hence, \emph{virtual models} are structuring units forming architectures while \emph{concepts} are the core entities. A concept has a set of \emph{properties} and \emph{behaviors}. \emph{Properties} can be either simple variables, roles (pointers to a modeling element in a \emph{virtual model} or an external technology-specific model), or properties bound to complex control graphs. \FML is designed to define not only the structure of virtual models but also the collection of actions that can be performed on them. These actions are called \emph{behaviors} and rely on behavioral primitives called \textsf{EditionAction}. These \emph{behaviors} can either be called or triggered by events. The reactive behaviors are useful when a federated model evolution needs to trigger a computation. Note that we do not exploit this possibility in the challenge.

>>>>

A \UML like representation of a simplified metamodel of \FML is provided in
Fig.~\ref{fig:mm}. \FML is a language designed to define virtual models. A
\emph{virtual model} is composed of a set of \emph{concepts} (named
\textsf{FlexoConcept} in Fig.~\ref{fig:mm}), while itself being a
\emph{concept}. Hence, \emph{virtual models} are structuring units forming
architectures while \emph{concepts} are the core entities. A concept has a set
of \emph{properties} (\textsf{FlexoProperty}) and \emph{behaviors}
(\textsf{FlexoBehaviour}). \emph{Properties} can be either simple variables,
roles (pointers to a modeling element in a \emph{virtual model} or an external
technology-specific model), or properties bound to complex control graphs. \FML
is designed to define not only the structure of virtual models but also the
collection of actions that can be performed on them. These actions are called
\emph{behaviors} and rely on behavioral primitives called
\textsf{EditionAction}. These \emph{behaviors} can either be called or
triggered by events. The reactive behaviors are useful when a federated model
evolution needs to trigger a computation. Note that we do not exploit this
possibility in the challenge.
